Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-10 draft/accordionComplexSurfaces.tex
remove ^ before \dual

Recall that there is a fixed bijection between the vertices of~$Q$, the arc in the dissection~$\dissection_{\bar Q}$ and the arcs in the dual dissection~$\dissection^\dual_{\bar Q}$.

@@

\begin{definition}\label{def: g-vectors for slaloms}
Let~$\alpha$ be a~$\dissection\dual_{\bar Q}$-slalom.
The~$\b{g}$-vector of~$\alpha$ is the vector in~$\R^{Q_0}$ counting the number of times that~$\alpha$ positively crosses each arc of~$\dissection\dual_{\bar Q}$ minus the number of times it crosses each arc negatively.
Here, a crossing is positive when~$\alpha$ leaves a face~$f^\dual$ to enter a face~$g^\dual$ with the vertex~$f$ being to its right (and thus with~$g$ being to its left).
Otherwise, the crossing is negative.
\end{definition}

@@

\begin{proposition}\label{prop: geometric interpretation of g- and c-vectors}
 Let~$\omega$ be a non-kissing walk in~$\bar Q$, and let~$\alpha$ be the corresponding curve on~$\surface(\bar Q)$, as in Definition~\ref{def:curveOfAWalk}.
 Recall from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that~$\alpha$ is both a~$\dissection_{\bar Q}$-accordion and a~$\dissection^\dual_{\bar Q}$-slalom.
 Let~$F$ be a non-kissing facet to which~$\omega$ belong.
 We also write~$F$ for the corresponding non-crossing facet in the slalom complex.
 Then:
 \begin{enumerate}
  \item The~$\b{g}$-vectors of the walk~$\omega$ and the accordion~$\alpha$ coincide.
  \item The~$\b{c}$-vectors of the walk~$\omega$ in~$F$ and the slalom~$\alpha$ in~$F$ concide.
 \end{enumerate}
\end{proposition}

>>>>

Recall that there is a fixed bijection between the vertices of~$Q$, the arc in the dissection~$\dissection_{\bar Q}$ and the arcs in the dual dissection~$\dissection\dual_{\bar Q}$.

@@

\begin{definition}\label{def: g-vectors for slaloms}
Let~$\alpha$ be a~$\dissection\dual_{\bar Q}$-slalom.
The~$\b{g}$-vector of~$\alpha$ is the vector in~$\R^{Q_0}$ counting the number of times that~$\alpha$ positively crosses each arc of~$\dissection\dual_{\bar Q}$ minus the number of times it crosses each arc negatively.
Here, a crossing is positive when~$\alpha$ leaves a face~$f\dual$ to enter a face~$g\dual$ with the vertex~$f$ being to its right (and thus with~$g$ being to its left).
Otherwise, the crossing is negative.
\end{definition}

@@

\begin{proposition}\label{prop: geometric interpretation of g- and c-vectors}
 Let~$\omega$ be a non-kissing walk in~$\bar Q$, and let~$\alpha$ be the corresponding curve on~$\surface(\bar Q)$, as in Definition~\ref{def:curveOfAWalk}.
 Recall from Lemma~\ref{lemm:curveOfAWalkIsAccordion} and Proposition~\ref{prop:accordionsSlaloms} that~$\alpha$ is both a~$\dissection_{\bar Q}$-accordion and a~$\dissection\dual_{\bar Q}$-slalom.
 Let~$F$ be a non-kissing facet to which~$\omega$ belong.
 We also write~$F$ for the corresponding non-crossing facet in the slalom complex.
 Then:
 \begin{enumerate}
  \item The~$\b{g}$-vectors of the walk~$\omega$ and the accordion~$\alpha$ coincide.
  \item The~$\b{c}$-vectors of the walk~$\omega$ in~$F$ and the slalom~$\alpha$ in~$F$ concide.
 \end{enumerate}
\end{proposition}
